Flight clustering for route detection and CO{\Large{\textsubscript{2}}} emissions

### 2016-10-23 paper/paper.tex
Title

\title{Title}
\author{Filippo Sestini \\ Vrije Universiteit Amsterdam \\ f.sestini@student.vu.nl \and
  Davide Dal Bianco \\ Vrije Universiteit Amsterdam \\ d.dalbianco@student.vu.nl}

@@

ADS-B messages are sent without any encryption and can be received and decoded
by anyone. We were able to obtain a dataset, provided by OpenSky network,
containing all the ADS-B messages sent by airplanes and collected by volunteers
during a time period spanning a week. The dataset includes data from September
18\textsuperscript{th} 2016 to September 24\textsuperscript{th} 2016, as
collected by about 70 sensors spread across western Europe. It is the purpose of
this paper to explain our approach in analyzing and extracting data from such
dataset. It is particularly intresting to see to which point data like the one
offered by OpenSky is suitable to get useful information about flights. In this
project, we concentrate on analyzing the air traffic and its patterns, and in
particular why try to discover standard routes between pairs of
airports, as well as flights that diverge from them.

>>>>

\title{Flight clustering for route detection and CO{\Large{\textsubscript{2}}} emissions}
\author{Filippo Sestini \\ Vrije Universiteit Amsterdam \\ f.sestini@student.vu.nl \and
  Davide Dal Bianco \\ Vrije Universiteit Amsterdam \\ d.dalbianco@student.vu.nl}

@@

ADS-B messages are sent without any encryption and can be received and decoded
by anyone. We were able to obtain a dataset, provided by OpenSky network,
containing all the ADS-B messages sent by airplanes and collected by volunteers
during a time period spanning a week. The dataset includes data from September
18\textsuperscript{th} 2016 to September 24\textsuperscript{th} 2016, as
collected by about 70 sensors spread across western Europe. It is the purpose of
this paper to explain our approach in analyzing and extracting data from such
dataset. It is particularly intresting to see to which point data like the one
offered by OpenSky is suitable to get useful information about flights. In this
project, we concentrate on analyzing the air traffic and its patterns, and in
particular we try to discover standard routes between pairs of
airports, as well as flights that diverge from them.
